Thermodynamic fragments for magic states in quantum computation

### 2021-03-08 magic_paper.tex
Added thoughts on how to incorporate our results in current literature

Given an $[[n,n',d]]$ error correcting code, a distillation protocol that achieves the process in~\cref{eq:test} requires
\begin{align}
	\epsilon' &\sim O((n\epsilon)^d) \\
	\frac{n}{n'} &\sim O(\log^\gamma{1/\epsilon'}),\ \gamma = \log_d{\left(\frac{n}{n'}\right)}
\end{align}

In~\cite{Bravyi2012,Hastings2018}, the asymptotic rate $O(\log^\gamma{1/\epsilon'})$ is called the \emph{distillation cost}.
\nick{These inequalities seem to be the other way around.}

>>>>

Given an $[[n,n',d]]$ error correcting code, a distillation protocol that achieves the process in~\cref{eq:test} requires
\begin{align}
	\epsilon' &\sim O\left((n\epsilon)^d\right) \\
	\frac{n}{n'} &\sim O(\log^\gamma{(1/\epsilon')}),\ \gamma = \log_d{\left(\frac{n}{n'}\right)}
\end{align}

In~\cite{Bravyi2012,Hastings2018}, the asymptotic rate $O(\log^\gamma{(1/\epsilon')})$ is called the \emph{distillation cost}.

There are many distillation protocols in the literature, e.g.~\cite{Bravyi2012,Hastings2018}, that involve a specific value of $\gamma$.
They should all satisfy
\begin{equation}\label{eq:rate_cost}
	\frac{1}{R(\epsilon, \epsilon', \beta)} \leq \frac{n}{n'} \sim O(\log^\gamma{(1/\epsilon')}).
\end{equation}
Therefore, given process parameters $n, n', \epsilon, \epsilon'$, we can scan through the stabilizer states to find a range of $\beta$ for which inequality~\cref{eq:rate_cost} is valid.
In principle, the higher the value of parameter $\gamma$, the lower the output error rate $\epsilon'$ can be while~\cref{eq:rate_cost} is still true.
In~\cite{Hastings2018} \nick{CITE MORE}, they report a value of $\gamma = 0.6779\dots$, while in~\cite{Krishna2019}, they report a scaling $\gamma = O(1/\log{d})$ with respect to the system's odd prime dimension $d$.
The latter tends to 0 asymptotically.

Furthermore, in~\cite{cit:bravyi,cit:prakash}, two different distillation protocols are proposed with output error rate scalings of the form 
\begin{equation}
	\epsilon' \propto (\alpha \epsilon)^{n^\xi},
\end{equation}
where $\alpha$ is some constant, $\xi = 1/\log_3{15} \approx 0.4$ in~\cite{cit:bravyi} for qubit codes and $\xi = 1/\log_3{19008} \approx 0.1$ for qutrit codes.
They also report a certain input threshold error rate $\epsilon_\star$ above which distillation is not possible.
A first requirement is that $\epsilon_\star \leq E(n'/n, \epsilon', \beta)$, but we can also again find a range of $\beta$ for which the inequality
\begin{equation}
	\epsilon \leq E\left(\frac{n'}{n}, \epsilon'(\epsilon), \beta \right)
\end{equation}
holds, given some distillation rate $n'/n$ and input error rate $\epsilon$.
